The Two Dualities of Computation: Negative and Fractional Types

### 2012-03-08 rational.tex
_

We leverage the basic idea of the above circuit, to collapse all
values that are not solutions to the specified isomorphic constraint
{{f}}. The operation {{f}} acts on some inputs and its adjoint
reconstructs the inputs from the outputs. While the output of {{f}}
may contain many components, its must contain a boolean indicating if
the input satisfy {{f}}. The special output wire is used to `control'
the negation of a boolean `control wire'. If the inputs do not satisfy
{{f}}, the control wire is negated.

>>>>

We leverage the basic idea of the above circuit, to collapse all
values that are not solutions to the specified isomorphic constraint
{{f}}. The contraint {{f}} checks the inputs to see if they match a
constraint -- in the case of the SAT solver, {{f}} would be the
circuit expressing the boolean expression to be satisfied.  While the
output of {{f}} may contain many components, its must contain a
boolean indicating if the input satisfy {{f}}. The operation {{f}}
acts on some inputs and its adjoint, {{f^{dagger} }}, reconstructs the
inputs from the outputs.  The `trick' is the following: the special
output wire is used to `control' the negation of a boolean `control
wire'.  If the inputs do not satisfy {{f}}, the control wire is
negated.
